Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Fix characters
Call tweet cohesion figure

```{r cohesion-in-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "Add more informative caption."}

# call figure 1 here

@@

This work was completed in part as coursework done by lead author M. Chiovaro in
the ``Applications of Nonlinear Time Series Analysis'' graduate course at the
University of Connecticut (co-taught by coauthor A. Paxton and Steven J.
Harrison).

>>>>

```{r cohesion-in-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = ""}

# call the image
knitr::include_graphics("./figs/cohesion-in-tweets.png")

@@

This work was completed in part as coursework done by lead author M. Chiovaro in
the “Applications of Nonlinear Time Series Analysis” graduate course at the
University of Connecticut (co-taught by coauthor A. Paxton and Steven J.
Harrison).
